### 2012-06-28 htdocs/user.tex
Comment on LB mobility
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1694 40876441-3496-0410-a613-a2fca35b2ae2

@@

There are a number of useful choices here. The key value
\texttt{twist} initialises a simple cholesteric with the
helical axis in the $z-$direction, whereas the values 
\texttt{cholesteric\_x\_y\_z} provide according initialisations 
with twist along the other axes.
The value \texttt{o8m} gives equilibrium BPI, \texttt{o2} gives BPII.
Another, cubic body-centered BP is obtained by the value \texttt{o5}.
Hexagonal BPs are initialised with \texttt{h2d, h3da} and \texttt{h3db}.\\
BPIII emerges from randomly positioned and oriented DTCs 
embedded into an isotropic or cholesteric environment.
It is initialised with the key value \texttt{bp3}, whereas the number
$N$ and radius $R$ of the DTCs and the type of the environment 
$ENV=\{0,1\}$, (0 = isotropic, 1 = cholesteric), is specified with the key value
\texttt{lc\_init\_bp3} $N\_R\_ENV$.\\
The appropriate choices for the other parameters must be made correspondingly.

An additional \texttt{lc\_q\_init\_amplitude} value sets the
scalar order parameter  `amplitude' in each case.

>>>>

Note that the relaxation time for the second distribution is
related to the mobility by $tau_\phi = M\rho_0/\Delta t + 1/2$.

@@

There are a number of useful choices here. The key value
\texttt{twist} initialises a simple cholesteric with the
helical axis in the $z-$direction, whereas the values 
\texttt{cholesteric\_x\_y\_z} provide similar initialisations 
with twist along the other axes.
The values \texttt{o8m} and \texttt{o2} give equilibrim BPI and BPII.
Another, cubic body-centered BP is obtained by the value \texttt{o5}.
Hexagonal BPs are initialised with \texttt{h2d, h3da} and \texttt{h3db}.\\
BPIII emerges from a start configuration of randomly positioned 
and oriented DTCs embedded into an isotropic or cholesteric environment.
This is initialised with the key value \texttt{bp3}, whereas the number
$N$ and radius $R$ of the DTCs and the type of the environment 
$ENV=\{0,1\}$, (0 = isotropic, 1 = cholesteric) is specified 
with the key value \texttt{lc\_init\_bp3} $N\_R\_ENV$. 
Note that calculations can become surprisingly unstable if the 
start configuration consits of too many and too large DTC-regions 
with respect to system size and decomposition.\\
The appropriate choices for the other parameters must be made correspondingly.

An additional \texttt{lc\_q\_init\_amplitude} value sets the
scalar order parameter  `amplitude' in each case. Typical
values are given in the input file. Values which are too large can
equally lead to instability.
